Male-biased sexual selection, but not sexual dichromatism, predicts speciation in birds

### 2021-01-18 Manuscript_Publication.Rmd
typo

![Estimates of the effect of individual sexual selection components included in the PPCA (paternal care, sexual size dimorphism and mating system) on three measures of speciation rate ($\lambda_{DR}$, $\lambda_{ND}$ and $\lambda_{BAMM}$). Estimates are presented as density intervals from pgls models on 300 phylogentic trees that used species with available data for these sexual selection measures (*n* = 2,465). The bar under each density ridge is the 95 % Highest Posterior Density Interval. Given that the mating system is a categorical variable, model estimates for three polygynous mating system levels are in reference to a striclty monogamous mating system (0% polygyny). \label{SS_components}](Figures/Individual_SS_Estimates.pdf)

>>>>

![Estimates of the effect of individual sexual selection components included in the PPCA (paternal care, sexual size dimorphism and mating system) on three measures of speciation rate ($\lambda_{DR}$, $\lambda_{ND}$ and $\lambda_{BAMM}$). Estimates are presented as density intervals from pgls models on 300 phylogentic trees that used species with available data for these sexual selection measures (*n* = 2,465). The bar under each density ridge is the 95 % Highest Posterior Density Interval. Given that the mating system is a categorical variable, model estimates for three polygynous mating system levels are in reference to a strictly monogamous mating system (0% polygyny). \label{SS_components}](Figures/Individual_SS_Estimates.pdf)

### 2021-01-18 Manuscript_Publication.tex
typo

\begin{figure}
\centering
\includegraphics{Figures/Individual_SS_Estimates.pdf}
\caption{Estimates of the effect of individual sexual selection
components included in the PPCA (paternal care, sexual size dimorphism
and mating system) on three measures of speciation rate
(\(\lambda_{DR}\), \(\lambda_{ND}\) and \(\lambda_{BAMM}\)). Estimates
are presented as density intervals from pgls models on 300 phylogentic
trees that used species with available data for these sexual selection
measures (\emph{n} = 2,465). The bar under each density ridge is the 95
\% Highest Posterior Density Interval. Given that the mating system is a
categorical variable, model estimates for three polygynous mating system
levels are in reference to a striclty monogamous mating system (0\%
polygyny). \label{SS_components}}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics{Figures/Individual_SS_Estimates.pdf}
\caption{Estimates of the effect of individual sexual selection
components included in the PPCA (paternal care, sexual size dimorphism
and mating system) on three measures of speciation rate
(\(\lambda_{DR}\), \(\lambda_{ND}\) and \(\lambda_{BAMM}\)). Estimates
are presented as density intervals from pgls models on 300 phylogentic
trees that used species with available data for these sexual selection
measures (\emph{n} = 2,465). The bar under each density ridge is the 95
\% Highest Posterior Density Interval. Given that the mating system is a
categorical variable, model estimates for three polygynous mating system
levels are in reference to a strictly monogamous mating system (0\%
polygyny). \label{SS_components}}
\end{figure}
